---
title: "Tutorial"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(mylogit)
library(stats)
library(datasets)
```


## Intro

This is a tutorial for R package `mylogit`. The main function `mylogit` is used
to fit a binary logistic regression model , along with `mylogit.predict` to get
the prediction value and class in a data set with fitted logistic model.
The example data set is `ToothGrowth` in package `datasets`. You may look up the 
help page for more information.

A comparison on both correctness and efficiency with the model fitted by `glm` 
will also be included.

## Usage
To use function `mylogit`:

Fit a logistic regression model where the response variable has 2 classes.
Default print out format is "brief", which provides basic statistics values
for logistic model, such as coefficient, deviance, AIC score.
```{r}
mylogit(supp ~ len,  data = ToothGrowth)
```

With format = "detailed", more details will be printed, including a table of
coefficients which contains estimate, standard error, z value, and p value.
```{r}
mylogit(supp ~ len,  data = ToothGrowth, format = "detailed")
```

With format = "nothing", there is no printing. You may need to declare a name
to store the model.
```{r}
logit = mylogit(supp ~ len,  data = ToothGrowth, format = "nothing")
```

Add another predictor variable.
```{r}
mylogit(supp ~ len + dose, data = ToothGrowth)
```

Add categorical predictor.
```{r}
mylogit(supp ~ len + as.factor(dose), data = ToothGrowth)
```

Add intersetion term.
```{r}
mylogit(supp ~ len + len*dose, data = ToothGrowth)
```

To make a class or value prediction, using `mylogit.predict`:

Predict the class for given test data 
```{r}
logit.pred = mylogit.predict(logit, ToothGrowth[1:30,])
logit.pred$predict.class
logit.pred$predict.value
```

If no new data set provided, it will return the fitted value and corresponding class
```{r}
logit.pred.2 = mylogit.predict(logit)
logit.pred.2
```

Actually, you will get the fitted value and predicted class in `mylogit`
```{r}
logit$fitted.values
logit$predict.class
```

You may choose to print prediction class when calling the function
```{R}
mylogit.predict(logit, print=TRUE)
```


## Comparsion
Compare with the logistic regression model fitted by `glm` function in `stats` R package:
Correctness Comparison
```{r}
myfit  = mylogit(supp~., ToothGrowth, "nothing")
rfit = glm(supp~., ToothGrowth, family="binomial")
```

```{r}
all.equal(myfit$coefficients, rfit$coefficients) # coefficient check
all.equal(myfit$fitted.values, rfit$fitted.values) # fitted value check
all.equal(myfit$deviance, rfit$deviance) # deviance check
all.equal(myfit$null.deviance, rfit$null.deviance) # null deviance check
all.equal(myfit$std.err, summary(rfit)$coef[,2], tolerance = 1e-5) # coefficient standard error check
all.equal(myfit$z.value, summary(rfit)$coef[,3], tolerance = 1e-5) # coefficient z value check
all.equal(myfit$p.value, summary(rfit)$coef[,4], tolerance = 1e-5) # coefficient p value check
all.equal(myfit$AIC, rfit$aic) # AIC check
all.equal(myfit$df, rfit$df.residual) # degrees of freedom check
all.equal(myfit$null.df, rfit$df.null) # null model degrees of freedom check
``` 

Efficiency Comparison
```{r}
myfit.time = system.time(for(i in 1:10) mylogit(supp~len+dose, data=ToothGrowth, format="nothing"))
rfit.time = system.time(for(i in 1:10) glm(supp~len+dose, data=ToothGrowth, family="binomial"))
print(myfit.time)
print(rfit.time)
```
Well, apparently, `mylogit` function is less efficient than the `glm` logistic
regression model in `family = "binomial"`.
